Human capital mediates natural selection in contemporary humans

### 2022-03-19 why-natural-selection.Rmd
fix one plot

library(drake)
library(magrittr)
library(dplyr)
library(forcats)
library(ggplot2)
library(tidyr)
library(santoku) # keep this after tidyr as it masks chop
library(purrr)
library(glue)
library(broom)
library(huxtable)
loadNamespace("scales")
loadNamespace("shades")

@@

  if (is.null(conf_int)) conf_int <- "conf.low" %in% names(dfr)
  confint_geom_segment <- if (conf_int) confint_geom_segment() else NULL

@@

  dfr %>% mutate(
    !! score_col := pretty_names(!! score_col),
    !! score_col := fct_reorder(!! score_col, estimate, order_abs(order_idx))
  ) %>% 
    rename(p = p.value) %>% 
    ggplot(aes(estimate, {{score_col}}, yend = {{score_col}}, 
               shape = {{fill_col}}, ...)) +
    my_vline + 
    confint_geom_segment +
    geom_point(size = 1.8, aes(color = {{fill_col}})) +
    geom_point(size = 0.7, color = "white", aes(alpha = p < 0.05/33)) +
    my_fill_scale(aesthetics = "color", n = n_cats, direction = fill_direction) +
    scale_shape_manual(values = 1:n_cats + 14) +
    my_labs() +
    my_theme() +
    scale_linetype_manual(name = "", values = c("95% c.i." = 1)) +
    scale_alpha_discrete(range = c(1, 0),
                         guide = guide_legend(
                           override.aes = list(
                             shape = c(1, 16),
                             color = "black",
                             alpha = 1,
                             size = 1.8
                           )
                         ))
}

@@

  if (n <= 2) {
    dots <- list(...)
    dots$direction <- NULL
    do.call(scale_colour_manual, c(list(values = fill_colors[1:n],
                                        aesthetics = aesthetics), 
                                   dots))
  } else {
    shades::lightness(scale_color_brewer(aesthetics = aesthetics, ...), 
                        shades::scalefac(0.85))
  }
}

@@

standard_ggplot(res_fe_fertility, fill_col = Regression, n_regs = n_regs,
                  fill_direction = -1) +
  guides(alpha = guide_legend(
                   override.aes = list(
                             shape = 1,
                             color = "black",
                             alpha = 1,
                             size = 1.8
                   )
                 )
  )

>>>>

library(drake)
library(magrittr)
library(dplyr)
library(forcats)
library(ggplot2)
library(tidyr)
library(santoku) # keep this after tidyr as it masks chop
library(purrr)
library(glue)
library(broom)
library(huxtable)
loadNamespace("scales")

@@

  if (is.null(conf_int)) conf_int <- "conf.low" %in% names(dfr)

@@

  confint_geom_segment <- if (conf_int) confint_geom_segment() else NULL

  dfr %>% mutate(
          !! score_col := pretty_names(!! score_col),
          !! score_col := fct_reorder(!! score_col, estimate, order_abs(order_idx))
        ) %>% 
        rename(p = p.value) %>% 
        ggplot(aes(estimate, {{score_col}}, yend = {{score_col}}, 
                     fill = {{fill_col}}, ..., colour = p < 0.05/{{n_regs}})) +
          my_vline + 
          confint_geom_segment +
          pval_geom_point(fill = if(rlang::quo_is_null(fill_col)) "steelblue") +
          pval_scale() +
          my_fill_scale(n = n_cats, direction = fill_direction) +
          my_labs() +
          my_theme() +
          scale_linetype_manual(name = "", values = c("95% c.i. uncorrected" = 1))

}

@@

  if (n <= 2) {
    dots <- list(...)
    dots$direction <- NULL
    do.call(scale_colour_manual, c(list(values = fill_colors[1:n],
                                        aesthetics = aesthetics), 
                                   dots))
  } else {
    scale_color_brewer(aesthetics = aesthetics, ...)
  }
}

@@

standard_ggplot(res_fe_fertility, fill_col = Regression, n_regs = n_regs,
                  fill_direction = -1)
